\thetitle

### 2009-02-19 paper/paper.tex
boilerplate tweaks
darcs-hash:20090219181245-d98fc-70b3ab13787a804da62441ff71e27b1a7248e2da.gz

\author{\eelis\thanks{Research carried out by the first author as part of the Master's programme in ``Foundations''} and \james \\
eelis@@eelis.net, james.mckinna@@cs.ru.nl}

\institute{Department of Computer Science, University of Nijmegen \\
P.O. Box 9010, 6500 GL Nijmegen, The Netherlands}

>>>>

\author{\eelis\thanks{Research carried out as part of the Radboud Master's programme in ``Foundations''} and \james \\
eelis@@eelis.net, james.mckinna@@cs.ru.nl}

\institute{
Institute for Computing and Information Sciences \\
Radboud University Nijmegen \\
Heijendaalseweg 135, 6525 AJ Nijmegen, The Netherlands}
